---
title: "Activity"
author: "Shraddha"
date: "11/05/2020"
output: html_document
---

```{r}
act<-read.csv("C:/Users/Shraddha/Desktop/activity.csv")
act
```

```{r}
dim(act)
str(act)
```

```{r}
sum(is.na(act))
act<-na.omit(act)
```

change date type to date class 
```{r}
act$date <- as.Date(as.character(act$date))
```

```{r}
summary(act)
```

## What is mean total number of steps taken per day?
```{r}
library(ggplot2)
total_steps <- tapply(act$steps, act$date, FUN=sum)
qplot(total_steps, binwidth=1000, xlab="total number of steps taken each day")
mean(total_steps)
median(total_steps)
```

## What is the average daily activity pattern?
```{r}
library(ggplot2)
averages <- aggregate(x=list(steps=act$steps), by=list(interval=act$interval),
                      FUN=mean)
ggplot(data=averages, aes(x=interval, y=steps)) +
    geom_line() +
    xlab("5-minute interval") +
    ylab("average number of steps taken")
```

On average across all the days in the dataset, the 5-minute interval contains
the maximum number of steps?
```{r}
averages[which.max(averages$steps),]
```

## Are there differences in activity patterns between weekdays and weekends?
First, let's find the day of the week for each measurement in the dataset. In
this part, we use the dataset with the filled-in values.

```{r}
weekday_weekend <- function(date) {
    day <- weekdays(date)
    if (day %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"))
        return("weekday")
    else if (day %in% c("Saturday", "Sunday"))
        return("weekend")
    else
        stop("invalid date")
}
act$date <- as.Date(act$date)
act$day <- sapply(act$date, FUN=weekday_weekend)
```

Now, let's make a panel plot containing plots of average number of steps taken
on weekdays and weekends.
```{r}
averages <- aggregate(steps ~ interval + day, data=act, mean)
ggplot(averages, aes(interval, steps)) + geom_line() + facet_grid(day ~ .) +
    xlab("5-minute interval") + ylab("Number of steps")
```

